XXXXX

### 2014-09-28 paper/paper1.tex
R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS

\begin{itemize}
	\item see R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
	\item covering approaches: ShEx, SPIN
\end{itemize}

\begin{itemize}
	\item instances of specific class must not have some object property
  \item OWL 2 DL: ObjectComplementOf ( DataSomeValuesFrom ( DataPropertyExpression rdfs:Literal ) )
	\item covering approaches: ShEx, SPIN
\end{itemize}

@@

A matching triple has any object except those excluded by the '-' operator.

>>>>

\begin{itemize}
	\item instances of specific class must not have some object property
  \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
	\item covering approaches: ShEx, SPIN
\end{itemize}

@@

\begin{ex}
<FeelingForce> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute xsd:string }
<JediMentor> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute 'good'^^xsd:string ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
    :mentorOf @<JediStudent> ,
    - :studentOf @<JediMentor> }
<JediStudent> {
    :feelingForce 'true'^^xsd:boolean ,
    :attitute 'good'^^xsd:string ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
    - :mentorOf @<JediStudent> ,
    :studentOf @<JediMentor> }
\end{ex}

individuals matching 'FeelingForce' and 'JediMentor' data shapes:

\begin{ex}
:Obi-Wan 
    :feelingForce 'true'^^xsd:boolean ;
    :attitute 'good'^^xsd:string ;
    :laserSwordColor 'blue'^^xsd:string ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
    :mentorOf :Anakin .
\end{ex}

individuals matching 'FeelingForce' and 'JediStudent' data shapes:

\begin{ex}
:Anakin 
    :feelingForce 'true'^^xsd:boolean ;
    :attitute 'good'^^xsd:string ;
    :laserSwordColor 'blue'^^xsd:string ,
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
    :studentOf :Obi-Wan . 
\end{ex}

\begin{itemize}
	\item analogous to R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
	\item covering approaches: ShEx, SPIN
\end{itemize}
